A Toolbox for Manipulating and Assessing Color Palettes

### 2020-11-07 pkg/colorspace/paper/Toolbox/article.Rmd
incorporate documentation of recently-added scico palettes (Hawaii, Batlow, Roma)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/colorspace@558 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

* `"Purple-Blue"` to `"Terrain 2"` are various palettes created during the development
  of \pkg{colorspace}, e.g., by @color:Zeileis+Hornik+Murrell:2009 or @color:Stauffer+Mayr+Dabernig:2015
  among others.
* `"Viridis"` to `"Inferno"` closely match the palettes that @color:Smith+VanDerWalt:2015
  developed for \pkg{matplotlib} and that gained popularity recently.
* `"Dark Mint"` to `"BrwnYl"` closely match palettes provided in \pkg{CARTO} [@color:CARTO].
* `"YlOrRd"` to `"Blues"` closely match \pkg{ColorBrewer.org} palettes [@color:Harrower+Brewer:2003].
* `"Lajolla"` and `"Turku"` closely match the scientific color maps of the same name by
  @color:Crameri:2018 and are intended for a black/dark background.

@@

* `"ArmyRose"` to `"Tropic"` closely match the palettes of the same name from \pkg{CARTO} [@color:CARTO].
* `"PuOr"` to `"Spectral"` closely match the palettes of the same name from \pkg{ColorBrewer.org} [@color:Harrower+Brewer:2003].
* `"Zissou 1"` closely matches the palette of the same name from \pkg{wesanderson} [@color:wesanderson].
* `"Cividis"` closely matches the palette of the same name from the \pkg{viridis} family [@color:viridis].
  Note that despite having two "arms" with blue vs.\ yellow colors and a low-chroma center color,
  this is probably better classified as a sequential palette due to the monotonic chroma going from dark to light.
  (See Section\ \ref{sec:approximations} for more details.)

>>>>

* `"Purple-Blue"` to `"Terrain 2"` are various palettes created during the development
  of \pkg{colorspace}, e.g., by @color:Zeileis+Hornik+Murrell:2009 or @color:Stauffer+Mayr+Dabernig:2015
  among others.
* `"Viridis"` to `"Inferno"` closely match the palettes that @color:Smith+VanDerWalt:2015
  developed for \pkg{matplotlib} and that gained popularity recently.
* `"Dark Mint"` to `"BrwnYl"` closely match palettes provided in \pkg{CARTO} [@color:CARTO].
* `"YlOrRd"` to `"Blues"` closely match \pkg{ColorBrewer.org} palettes [@color:Harrower+Brewer:2003].
* `"Lajolla"` to `"Batlow"` closely match the scientific color maps of the same name by
  @color:Crameri:2018 and the first two of these are intended for a black/dark background.

@@

* `"ArmyRose"` to `"Tropic"` closely match the palettes of the same name from \pkg{CARTO} [@color:CARTO].
* `"PuOr"` to `"Spectral"` closely match the palettes of the same name from \pkg{ColorBrewer.org} [@color:Harrower+Brewer:2003].
* `"Zissou 1"` closely matches the palette of the same name from \pkg{wesanderson} [@color:wesanderson].
* `"Cividis"` closely matches the palette of the same name from the \pkg{viridis} family [@color:viridis].
  Note that despite having two "arms" with blue vs.\ yellow colors and a low-chroma center color,
  this is probably better classified as a sequential palette due to the monotonic chroma going from dark to light.
  (See Section\ \ref{sec:approximations} for more details.)
* `"Roma"` closely matches the palette of the same name by @color:Crameri:2018.
